---
title: "VG_Chartz_analysis"
author: "Brennan Donnell"
date: "12/15/2018"
output: html_document
---

[Shinyapp.io](https://bjn82.shinyapps.io/VG_Sales/)

I've picked the [Video Games sales dataset](https://www.kaggle.com/gregorut/videogamesales). 

Reason: I like video games, particularly old systems. It interests me to see how the technology has shifted. The rise and fall of developers such as Sega, the flaws and features of consoles, and more. 

```{r imports, warning=FALSE, message=FALSE, error=FALSE}
library(dplyr)
library(stringr)
library(rebus)
library(data.table)
library(ggplot2)
library(lubridate)
library(plotly)
library(markdown)
library(shiny)
```

After loading in the necessary libraries, I then read in the data through `fread` and converted it to a tibble. 
```{r load_data}
df <- tbl_df(fread('vgsales.csv', 
                     header=T, 
                     fill=TRUE, 
                     sep=","))
```

Once the data is read into the tibble, named *df*, I analyzed the data to see if there were any missing values. 

```{r na_search}
colSums(is.na(df))
```

No missing values in sight! Amazing! But, let's make certain of it by searching for string values of *N/A*.  

```{r table_year}
for (col in 1:length(df)) {
  na_count <- sum(df[col] == 'N/A' )
  unknown_count <-sum(df[col] == 'Unknown' )
  ifelse(na_count ==0, NA, print(str_c(names(df[col]), ': ', na_count," values of 'N/A'")))
  ifelse(unknown_count ==0, NA, print(str_c(names(df[col]), ': ', unknown_count," values of 'Unknown'")))
}
```

So despite there being no *NA* values, there are still some missing values. 
First thing to do is to remove NAs for columns. While there could be many reasons for the year missing, it could likely be due to 
* not being released as of when the data was published
* A game that was cancelled

Also, to look at games where there is either no info about a publisher or the publisher is unknown. 

```{r clean_data}
df_filt <- df %>% 
  filter(Year != 'N/A') %>% 
  filter(Publisher != 'N/A')%>% 
  filter(Publisher!= 'Unknown')

df_filt$Year <- as.numeric(df_filt$Year)
df_filt <- df_filt %>% 
  filter(Year <= year(Sys.Date()))

rm(df)

region_sales <- 7:11
names(region_sales) <- names(df_filt[7:11])
```

Now, I want to track games by if they are part of a series. e.g.: Mario, Halo, Metal Gear, Zelda, etc. 
the code for this is ugly, and it isn't perfect. There are a few games that don't get put into the correct series, and I know I'm missing some series. In a future version of this, I'm planning on having a better way to identify series. 

```{r series_data, echo=FALSE}
seg_9 <- function(x){
  ifelse(grepl('God of War',x) | grepl('God Of War', x), 'God of War',
         ifelse(grepl('Tropico',x),'Tropico', 
                ifelse(grepl('Tony Hawk',x), 'Tony Hawk Game', 
                       ifelse(grepl('Fable',x), 'Fable', 
                              ifelse(grepl('TMNT',x) | grepl('Teenage Mutant', x), "TMNT", 
                                     ifelse(grepl('Def Jam', x), 'Def Jam', 
                                            ifelse(grepl('Hyperdimens', x), 'Hyperdimension Neptunia', 
                                                   ifelse(grepl('PES',x) | grepl('Pro Evolution Soccer', x), 'PES', 
                                                          ifelse(grepl('Ace Combat', x), "Ace Combat", 
                                                                 ifelse(grepl("Army Men", x), "Army Men", 
                                                                        ifelse(grepl('SOCOM', x), 'SOCOM', 
                                                                               ifelse(grepl('KillZone', x), 'Killzone', 
                                                                                      ifelse(grepl('Army of Two', x) | grepl('Army Of Two', x), 'Army of Two', 
                                                                                             ifelse(grepl('Duke N', x), 'Duke Nukem',          ifelse(grepl('NFL Blitz', x), 'NFL Blitz', 
                                                                                                                                                      ifelse(grepl('Miku', x) | grepl('Mirai', x), 'Hatsune Miku', 
                                                                                                                                                             ifelse(grepl('NASCAR',x), 'NASCAR game', ifelse(grepl('DarkStalker', x), 'Darkstalkers', 
                                                                                                                                                                                                             ifelse(grepl('LEGO',x), 'LEGO', 
                                                                                                                                                                                                                    ifelse(grepl('Final Fight',x), 'Final Fight', 
                                                                                                                                                                                                                           ifelse(grepl('Sailor Moon', x), 'Sailor Moon', 
                                                                                                                                                                                                                                  ifelse(grepl('Shrek',x),'Shrek',
                                                                                                                                                                                                                                         ifelse(grepl('Scooby',x),'Scooby-Doo',
                                                                                                                                                                                                                                                ifelse(grepl('Lost Planet',x),'Lost Planet',
                                                                                                                                                                                                                                                       ifelse(grepl('Corpse Party',x),'Corpse Party',
                                                                                                                                                                                                                                                              ifelse(grepl('Backyard',x),'Backyard Sports',
                                                                                                                                                                                                                                                              ifelse(grepl('Leisure Suit',x),'Leisure Suit Larry',
                                                                                                                                                                                                                                                                     ifelse(grepl('Dragon Warrior',x),'Dragon Warrior',
                                                                                                                                                                                                                                                                            ifelse(grepl('Monster Jam',x),'Monster Jam',
                                                                                                                                                                                                                                                                                   ifelse(grepl('no Stafi',x),'Stafi',
                                                                                                                                                                                                                                                                                          ifelse(grepl('Call of Juarez',x),'Call of Juarez',
                                                                                                                                                                                                                                                                                                 ifelse(grepl('Chibi-',x),'Chibi-Robo',
                                                                                                                                                                                                                                                                                                        ifelse(grepl('Transformer',x),'Transformers',
                                                                                                                                                                                                                                                                                                               ifelse(grepl('NCAA',x),'NCAA',
                                                                                                                                                                                                                                                                                                                      ifelse(grepl('Tetris',x),'Tetris game',
                                                                                                                                                                                                                                                                                                                             ifelse(grepl('Robotech',x),'Robotech',
                                                                                                                                                                                                                                                                                                                                    ifelse(grepl('Pikmin',x), 'Pikmin', 'other')))))))))))))))))))))))))))))))))))))
}
seg_8 <- function(x){
  ifelse(grepl('Elder Scrolls',x),'Elder Scrolls',
         ifelse(grepl('Idolmaster',x) | grepl('IdolMaster',x) | grepl('Idolm@',x)|grepl('IdolM@',x),'Idolmaster',
                ifelse(grepl('King of Fighters',x) | grepl('King Of Fighter',x),'KoF',
                       ifelse(grepl('Lord of the Rings',x) | grepl('Hobbit',x),'LotR',
                              ifelse(grepl('Simpsons',x),'The Simpsons',
                                     ifelse(grepl('The Sims',x),'The Sims',
                                            ifelse(grepl('Time Crisis',x),'Time Crisis',
                                                   ifelse(grepl('Toukiden',x),'Toukiden',
                                                          ifelse(grepl('Trauma',x),'Trauma Center',
                                                                 ifelse(grepl('Turok',x),'Turok',
                                                                        ifelse(grepl('Twisted Metal',x),'Twisted Metal',
                                                                               ifelse(grepl('Unreal',x),'Unreal Tournament',
                                                                                      ifelse(grepl('Warhammer',x),'Warhammer',
                                                                                             ifelse(grepl('Warriors Orochi',x),'Warriors Orochi',
                                                                                                    ifelse(grepl('Wolfenstein',x),'Wolfenstein',
                                                                                                           ifelse(grepl('Warcraft',x),'WoW',
                                                                                                                  ifelse(grepl('Worms',x),'Worms',
                                                                                                                         ifelse(grepl('X-Men',x),'X-Men',
                                                                                                                                ifelse(grepl('Yakuza',x),'Yakuza',
                                                                                                                                       ifelse(grepl('Yoshi',x),'Yoshi',
                                                                                                                                              ifelse(grepl('Yu-Gi-Oh!',x),'Yu-Gi-Oh!',
                                                                                                                                                     ifelse(grepl('Touhou',x),'Touhou',
                                                                                                                                                            ifelse(grepl('Uncharted',x),'Uncharted',
                                                                                                                                                                   ifelse(grepl('Tom Clancy',x),'Tom Clancy',seg_9(x)
                                                                                                                                                     ))))))))))))))))))))))))
}
seg_7 <- function(x){
  ifelse(grepl('Romance of the',x),"Romance of the Three Kingdoms",
         ifelse(grepl('Rune Factory',x),'Rune Factory',
                ifelse(grepl('Saints Row',x),'Saints Row',
                       ifelse(grepl('Sakura Wars',x),'Sakura Wars',
                              ifelse(grepl('Samurai Warriors',x),'Samurai Warriors',
                                     ifelse(grepl('Senran Kagura',x),'Senran Kagura',
                                            ifelse(grepl('Serious Sam',x),'Serious Sam',
                                                   ifelse(grepl('Shin Megami', x) | grepl('SMT',x)|grepl('Megami Tensei',x),'SMT',
                                                          ifelse(grepl('Silent Hill',x),'Silent Hill',
                                                                 ifelse(grepl('Skylander',x),'Skylanders',
                                                                        ifelse(grepl('SoulCalibur',x),'Soul Calibur',
                                                                               ifelse(grepl('Spider-',x),'Spider-Man',
                                                                                      ifelse(grepl('SpongeBob',x),'SpongeBob',
                                                                                             ifelse(grepl('Spyro',x),'Spyro',
                                                                                                    ifelse(grepl('SSX',x),'SSX',
                                                                                                           ifelse(grepl('Star Fox',x),'Star Fox',
                                                                                                                  ifelse(grepl('Star Trek',x),'Star Trek',
                                                                                                                         ifelse(grepl('Star Ocean',x),'Star Ocean',
                                                                                                                                ifelse(grepl('Street Fighter',x),'Street Fighter',
                                                                                                                                       ifelse(grepl('Suikoden',x),'Suikoden',
                                                                                                                                              ifelse(grepl('Monkey Ball',x),'Monkey Ball',
                                                                                                                                                     ifelse(grepl('Super Robot',x),'Super Robot',
                                                                                                                                                            ifelse(grepl('Smash Bros',x),'Smash Bros',
                                                                                                                                                                   ifelse(grepl('Tales of',x),'Tales of',
                                                                                                                                                                          ifelse(grepl('Tamagotchi',x),'Tamagotchi',
                                                                                                                                                                                 ifelse(grepl('Tekken',x),'Tekken',seg_8(x)
                                                                                                                                                                                 ))))))))))))))))))))))))))
  
}
seg_6 <- function(x){
  ifelse(grepl('Just Dance',x),'Just Dance',
         ifelse(grepl('Kingdom Hearts',x),'Kingdom Hearts',
                ifelse(grepl('Kirby',x),'Kirby',
                       ifelse(grepl('Tomb Raider',x)|grepl('Lara Croft',x),'Tomb Raider',
                              ifelse(grepl('LittleBigPlanet',x),'LBP',
                                     ifelse(grepl('Madden',x),'Madden',
                                            ifelse(grepl('Sonic',x)|grepl('Knuckles',x)|grepl('Tails',x),'Sonic',
                                                   ifelse(grepl('Mass Effect',x),'Mass Effect',
                                                          ifelse(grepl('Max Payne',x),'Max Payne',
                                                                 ifelse(grepl('Medal of Honor',x),'Medal of Honor',
                                                                        ifelse(grepl('Mega Man',x),'Mega Man',
                                                                               ifelse(grepl('Metal Gear',x),'Metal Gear',
                                                                                      ifelse(grepl('Metal Slug',x),'Metal Slug',
                                                                                             ifelse(grepl('Metroid',x),'Metroid',
                                                                                                    ifelse(grepl('Midnight Club',x),'Midnight Club',
                                                                                                           ifelse(grepl('MonHun',x)|grepl('Monster Hunter',x),'Monster Hunter',
                                                                                                                  ifelse(grepl('Mortal Kombat',x),'Mortal Kombat',
                                                                                                                         ifelse(grepl('Mother ',x)|grepl('EarthBound',x),'Mother',
                                                                                                                                ifelse(grepl('Naruto',x),'Naruto',
                                                                                                                                       ifelse(grepl('Need for Speed',x)|grepl('Need For Speed',x),'NfS',
                                                                                                                                              ifelse(grepl('Ninja Gaiden',x),'Ninja Gaiden',
                                                                                                                                                     ifelse(grepl('PAC-MAN',x)|grepl('Pac-Man',x),'Pac-Man',
                                                                                                                                                            ifelse(grepl('Persona',x) & !grepl('Personal',x),'Persona',
                                                                                                                                                                   ifelse(grepl('Phantasy Star',x),'Phantasy Star',
                                                                                                                                                                          ifelse(grepl('Ace Attorney',x),'Ace Attorney',
                                                                                                                                                                                 ifelse(grepl('Prince of Persia',x),'Prince of Persia',
                                                                                                                                                                                        ifelse(grepl('Layton',x),'Professor Layton',
                                                                                                                                                                                               ifelse(grepl('Quake',x),'Quake',
                                                                                                                                                                                                      ifelse(grepl('Ratchet',x),'Ratchet & Clank',
                                                                                                                                                                                                             ifelse(grepl('Rayman',x),'Rayman',
                                                                                                                                                                                                                    ifelse(grepl('Red Dead',x),'Red Dead Redemption',
                                                                                                                                                                                                                           ifelse(grepl('Red Faction',x),'Red Faction',
                                                                                                                                                                                                                                  ifelse(grepl('Resident Evil',x),'RE',seg_7(x))
                                                                                                                                                                                                                           ))))))))))))))))))))))))))))))))
}
seg_5 <- function(x){
  ifelse(grepl('Ape Escape',x),'Ape Escape',
  ifelse(grepl('Far Cry',x),'Far Cry',
         ifelse(grepl('Farming Simulator',x),'Farming Simulator',
                ifelse(grepl('Fatal Frame',x),'Fatal Frame',
                       ifelse(grepl('Fire Emblem',x),'Fire Emblem',
                              ifelse(grepl('Forza',x),'Forza',
                                     ifelse(grepl('Frogger',x),'Frogger',
                                            ifelse(grepl('Gears of War',x),'Gears of War',
                                                   ifelse(grepl('God Eater',x),'God Eater',
                                                          ifelse(grepl('Golden Sun',x),'Golden Sun',
                                                                 ifelse(grepl('Rock Band',x),'Rock Band',
                                                                        ifelse(grepl('Guild Wars',x),'Guild Wars',
                                                                               ifelse(grepl('Guilty Gear',x),'Guilty Gear',
                                                                                      ifelse(grepl('Guitar Hero',x),'Guitar Hero',
                                                                                             ifelse(grepl('Gundam',x),'Gundam',
                                                                                                    ifelse(grepl('Half-Life',x),'Half-Life',
                                                                                                           ifelse(grepl('Harvest Moon',x),'Harvest Moon',
                                                                                                                  ifelse(grepl('Hitman',x) & !grepl('Reborn!',x),'Hitman',
                                                                                                                         ifelse(grepl('Indiana Jones',x),'Indiana Jones',
                                                                                                                                ifelse(grepl('Just Cause',x),'Just Cause',seg_6(x))
                                                                                                                         )))))))))))))))))))
}
seg_4 <- function(x){
  ifelse(grepl('CSI',x),'CSI',
         ifelse(grepl('Custom Robo',x),'Custom Robo',
                ifelse(grepl('Dance Dance Revolution',x),'DDR',
                       ifelse(grepl('Dark Souls', x), 'Dark Souls',
                              ifelse(grepl('Darksiders',x), 'Darksiders',
                                     ifelse(grepl('Dead Island',x),'Dead Island',
                                            ifelse(grepl('Dead or Alive',x),'DoA',
                                                   ifelse(grepl('Dead Rising',x),'Dead Rising',
                                                          ifelse(grepl('Dead Space',x),'Dead Space',
                                                                 ifelse(grepl('Dead to Rights',x),'Dead to Rights',
                                                                        ifelse(grepl('Deus Ex',x),'Deus Ex',
                                                                               ifelse(grepl('Devil May Cry',x),'DMC',
                                                                                      ifelse(grepl('Diablo',x),'Diablo',
                                                                                             ifelse(grepl('Digimon',x),'Digimon',
                                                                                                    ifelse(grepl('Disgaea',x),'Disgaea',
                                                                                                           ifelse(grepl('Doom',x) & !grepl('of Doom',x),'Doom',
                                                                                                                  ifelse(grepl('Dragon Age',x),'Dragon Age',
                                                                                                                         ifelse(grepl('Dragon Ball',x),'Dragon Ball',
                                                                                                                                ifelse(grepl('Dragon Quest',x),'Dragon Quest',
                                                                                                                                       ifelse(grepl('Dynasty Warriors',x),'Dynasty Warriors',
                                                                                                                                              ifelse(grepl('Etrian',x),'Etrian Odyssey',
                                                                                                                                                     ifelse(grepl('F-Zero',x),'F-Zero',
                                                                                                                                                            ifelse(grepl('F.E.A.R',x),'FEAR',
                                                                                                                                                                   ifelse(grepl('Fallout',x),'Fallout',
                                                                                                                                                                          ifelse(grepl("Assassins's",x),"Assassin's Creed",
                                                                                                                                                                                 ifelse(grepl('Armored Core',x),'Armored Core',
                                                                                                                                                                                        ifelse(grepl('Atelier',x),'Atelier',
                                                                                                                                                                                               ifelse(grepl('Batman',x),'Batman',
                                                                                                                                                                                                      ifelse(grepl("Assassin's",x),"Assassin's Creed", seg_5(x)
                                                                                                                                                                   )))))))))))))))))))))))))))))
}
seg_3 <- function(x){
  ifelse(grepl('BioShock',x),'BioShock',
         ifelse(grepl('BlazBlue',x) | grepl('Blazblue',x),'BlazBlue',                                                                                       
                ifelse(grepl('Bleach',x),'Bleach',
                       ifelse(grepl('Bloody Roar',x),'Bloody Roar',
                              ifelse(grepl('Bomberman',x),'Bomberman',
                                     ifelse(grepl('Borderlands',x),'Borderlands',
                                            ifelse(grepl('Bratz',x),'Bratz',
                                                   ifelse(grepl('Breath of Fire',x),'Breath of Fire',
                                                          ifelse(grepl('Broken Sword',x),'Broken Sword',
                                                                 ifelse(grepl('Brothers in Arms',x)|grepl('Brothers In Arms',x),'Brothers in Arms',
                                                                        ifelse(grepl('Burnout',x),'Burnout',
                                                                               ifelse(grepl('Buzz!',x),'Buzz!',
                                                                                      ifelse(grepl('Cabela',x),'Cabela',
                                                                                             ifelse(grepl('Carmen Sandiego',x),'Carmen Sandiego',
                                                                                                    ifelse(grepl('Castlevania',x),'Castlevania',
                                                                                                           ifelse(grepl('Donkey Kong',x)|grepl('Diddy Kong',x), 'Donkey Kong',
                                                                                                                  ifelse(grepl('Clock Tower',x),'Clock Tower',
                                                                                                                         ifelse(grepl('Command & Conquer',x),'Command & Conquer',
                                                                                                                                ifelse(grepl('Cooking Mama',x),'Cooking Mama',
                                                                                                                                       ifelse(grepl('Crash',x),'Crash Bandicoot',
                                                                                                                                              ifelse(grepl('Crazy Taxi',x), 'Crazy Taxi',
                                                                                                                                                     ifelse(grepl('Crysis',x),'Crysis', seg_4(x))
                                                                                                                                              )))))))))))))))))))))
}
seg_2 <- function(x){
  ifelse(grepl('Animal Crossing',x), 'Animal Crossing',
         ifelse(grepl('Gran Turismo',x), 'Gran Turismo',
                ifelse(grepl('Star Wars',x), 'Star Wars',
                       ifelse(grepl('FIFA',x), 'FIFA',
                              ifelse(grepl('Battlefield',x),'Battlefield',
                                     ifelse(grepl('.hack',x, fixed = TRUE), '.hack',
                                            ifelse(grepl('Super Robot Wars',x),'Super Robot Wars',
                                                   ifelse(grepl('Battle of Giants',x),'Battle of Giants',
                                                          ifelse(grepl('Battle Spirits',x),'Battle Spirits',
                                                                 ifelse(grepl('Battlestations',x),'Battlestations',
                                                                        ifelse(grepl('Bayonetta',x),'Bayonetta',
                                                                               ifelse(grepl('BeatMania',x),'BeatMania',
                                                                                      ifelse(grepl('Katamari',x),'Katamari',
                                                                                             ifelse(grepl('Ben 10',x),'Ben 10',
                                                                                                    ifelse(grepl('Beyblade',x)|grepl('BeyBlade',x),'Beyblade',
                                                                                                           ifelse(grepl('Banjo',x) & !grepl('Sonic',x) & !grepl('Geass',x),'Banjo Kazooie',seg_3(x))
                                                                                             )))))))))))))))
}
seg_1 <- function(x){
  ifelse(grepl('Mario Kart', x), 'Mario Kart', 
         ifelse(grepl('Mario Party', x), 'Mario Party', 
                ifelse(grepl('Mario Tennis',x),'Mario Tennis',
                       ifelse(grepl('Mario & Sonic',x),'Mario & Sonic',
                              ifelse(grepl('Zelda',x), 'Zelda', 
                                     ifelse(grepl('Mario', x) | grepl('Luigi', x) | grepl('Captain Toad',x) | grepl('Wario',x) & !grepl('Marionette',x), 'Mario',
                                            ifelse(grepl('Pokemon', x) | grepl('Pokémon',x), 'Pokemon',
                                                   ifelse(grepl('Halo', x), 'Halo', 
                                                          ifelse(grepl('Final Fantasy',x), 'Final Fantasy',
                                                                 ifelse(grepl('Call of Duty',x), 'Call of Duty', 
                                                                        ifelse(grepl('Grand Theft Auto', x),'GTA',seg_2(x))
                                                                 ))))))))))
}


series_seg <- function(x){
  seg_1(x)
}


df_filt$Series <-
  sapply(df_filt$Name, series_seg) #that's how sapply works. look up notes.

```


```{r top_ten_platform}
df_plat <- df_filt %>% 
  group_by(Platform) %>% 
  summarise(n=n())


top_sales <- function(vg_sys){
  df_vg <- df_filt %>%
    filter(Platform == vg_sys) %>%
    arrange(Rank)
  return(head(df_vg, n = 10))
}

```


The purpose of this part is to show how many games in the chart corresponded to a given genre for all platforms. It was my dad's idea, and as the chunk is named, a last minute idea. 
```{r last_Minute}
df_genre <- df_filt %>% 
  filter(Genre == 'Sports') %>% 
  group_by(Platform) %>% 
  summarise(n=n())

ggplot(data = df_genre, aes(x=Platform, y=n, fill = Platform)) + geom_col() + theme_classic()
```



```{r shiny_app}
ui_full <- navbarPage(
  title = "Video Games",
  tabPanel(title = "Readme",
           includeMarkdown("readme.md")
  ),
  tabPanel(title = "Scatterplot",
           sidebarLayout(
             sidebarPanel(
               radioButtons(
                 inputId = "region_ui",
                 label = "Select Region",
                 choices = names(region_sales),
                 selected = names(region_sales[1]),
                 inline = TRUE),
               selectInput(
                 inputId = "series_ui",
                 label = "Select Series",
                 choices = unique(df_filt$Series),
                 selected = unique(df_filt$Series)[2])
             ),
             mainPanel(
               h2(str_c("Scatterplot of Global Sales by Platform",
                        " for a given series")),
               plotlyOutput(outputId = "scatter")
             )
           )
  ),
  tabPanel(title = "Publisher Sales Chart",
           sidebarLayout(
             sidebarPanel(
               selectInput(
                 inputId = "publisher_ui",
                 label = "Select Publisher",
                 choices = unique(df_filt$Publisher),
                 selected = unique(df_filt$Publisher)[1])
             ),
             mainPanel(
               h2("Barchart of frequency of genre for a given publisher"),
               plotOutput(outputId = "bar")
             )
           )
  ),
  tabPanel(title = "Console Sales Table",
           sidebarLayout(
             sidebarPanel(
               sliderInput(
                 inputId = "range",
                 label = "Year range",
                 min = min(df_filt$Year),
                 max = max(df_filt$Year),
                 value = c(1995, 2005),
                 sep = ""
               )
             ),
             mainPanel(
               h2("Console game sales throughout the years"),
               splitLayout(
                 tableOutput(outputId = "table"),
                 plotOutput(outputId = "table_bar"))))
  ),
  tabPanel(title = 'Sales by Genre',
           sidebarLayout(
             sidebarPanel(
               selectInput(
                 inputId = 'gen',
                 label = "Select Genre",
                 choices = unique(df_filt$Genre),
                 selected = unique(df_filt$Genre)[1]
               )
             ),
             mainPanel(
               h2("Plot of genre sales by platform"),
               plotOutput(
                 outputId = 'gen_bar'
               )
             )
           )
  ),
  tabPanel(title = "Facts",
           sidebarLayout(
             sidebarPanel(
               selectInput(
                 inputId = "sys",
                 label = "Select System",
                 choices = unique(df_filt$Platform))
             ),
             mainPanel(
               tabsetPanel(
                 tabPanel(title = "Facts & Info",
                          splitLayout(
                            imageOutput(outputId = "img"),
                            htmlOutput(outputId = "txt")
                          )
                 ),
                 tabPanel(title = "Table",
                          tableOutput(outputId = "tbl")
                          )
                 )
               )
             )
           )
)


server_full <- function(input, output){
  filtered_data_1 <- reactive({
    filter(
      df_filt,
      Series == input$series_ui)})
  filtered_data_2 <- reactive({
    as.data.frame(table(filter(
      df_filt,
      Publisher == input$publisher_ui)$Genre))})
  filtered_data_3 <- reactive({
    filter(
      df_filt,
      Year >= min(input$range) & Year <= max(input$range))})
  filtered_data_4 <- reactive({top_sales(input$sys)})
  filtered_data_5 <- reactive({
    df_out <- df_filt %>% 
      filter(Genre == input$gen) %>% 
      group_by(Platform) %>% 
      summarise(n=n())
    df_out
  })
  filtered_text <- reactive(input$sys)
  output$scatter <- renderPlotly({
    ggplotly(
      ggplot(
        filtered_data_1(),
        aes_string(
          x = "Platform",
          y = input$region_ui)) +
        geom_point(aes(colour = Genre, text=Name)) +
        theme_classic() +
        theme(axis.text.x = element_text(angle = 60, hjust = 1)))}
  )
  output$bar <- renderPlot({
    ggplot(
      data = filtered_data_2(),
      aes(
        x = Var1,
        y = Freq,
        fill = Var1)) +
      geom_col() +
      labs(
        title = names(input$publisher_ui),
        x = "Genre",
        y = "Frequency") +
      scale_fill_hue(h = c(0,360)) +
      theme_classic() +
      theme(axis.text.x = element_text(angle = 60, hjust = 1))}
  )
  output$gen_bar <- renderPlot({
    ggplot(
      data = filtered_data_5(),
      aes(
        x = Platform, 
        y = n, 
        fill = Platform, 
      )
    ) + 
      geom_col() + 
      labs(x = "System", y = "Games") +
        scale_fill_hue(h = c(0,360)) +
        theme_classic() +
        theme(axis.text.x = element_text(angle = 60, hjust = 1))
  })
  output$table <- renderTable(
    {
      tb <- filtered_data_3() %>%
        group_by(Platform) %>%
        summarise(NA_Sales = n()) %>%
        arrange(desc(NA_Sales))
      tb
    },
    striped = TRUE, 
    hover = TRUE
  )
  output$table_bar <- renderPlot(
    {
      ggplot(
        data = filtered_data_3(),
        aes(
          x = Platform,
          y = NA_Sales,
          fill = Platform)
      ) +
        geom_col() +
        labs(x = "System", y = "Sales") +
        scale_fill_hue(h = c(0,360)) +
        theme_classic() +
        theme(axis.text.x = element_text(angle = 60, hjust = 1))
    }
  )
  output$img <- renderImage({
    filename <- normalizePath(file.path('./www',
                                        str_c(filtered_text(),'.jpg')))
    
    # Return a list containining the filename
    list(src = filename)
  },deleteFile = FALSE )
  output$txt <- renderText(
    includeMarkdown(
      str_c('Systems/',filtered_text(),'.md')))
  output$tbl <- renderTable(
    {filtered_data_4()},
    striped = TRUE,
    hover = TRUE
  )
}

shinyApp(ui = ui_full, server = server_full)
```

## Insights from the project? 

1. Games that came bundled with systems or accessories were generally the top-selling games for that platform
 + e.g.: *Wii Sports* & *Kinect Adventures*. 
2. Not all systems had a top ten. And some systems that were included in the data were never released in North America
 + e.g.: the WonderSwan, TG16. 
3. Certain publishers tended to put out more of certain types of games, though there is a logical explanation to it. 
 + Electronic Arts puts out a lot of sports games, although they hold the licenses to many yearly sports games such as *Madden*. 
 + SquareSoft (Now Square Enix) and Atlus put out primarily JRPGs
4. *Minecraft* for the PS Vita (PSV) was the top-selling PS Vita game, selling more units in Japan and Europe than in North America. 
 